Meta RL analyses

### 2018-12-18 meta_RL_analyses.Rmd
Starting to set up for some nicer plots, including baseliens

# utils

@@

@@

```{r}
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one", "nometa_only_one")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

>>>>

# utils and setup

@@

plot themes
```{r}
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```

```{r}
summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +
    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
    geom_point(stat="summary", fun.y=mean, size=2) +
    geom_errorbar(stat="summary", 
                  fun.ymin=function(x) {mean(x) - 1.96*sd(x)/sqrt(length(x))},
                  fun.ymax=function(x) {mean(x) + 1.96*sd(x)/sqrt(length(x))},
                  width=0.25) +
    scale_color_brewer(palette=palette)

  if (!is.null(baseline_data)) {
    p = p + 
      annotate("segment",
               x=(1:5)-0.5, xend=(1:5)+0.5,
               y=simple_baselines$expected_reward,
               yend=simple_baselines$expected_reward,
               linetype=3, alpha=0.5) 
  }

  return(p)
}
```

```{r}
baseline_data = read_csv("baseline_data.csv") %>%
  mutate(game_type = str_extract(game, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game),
         black_valuable = grepl("bv_1", game),
         suits_rule = grepl("sr_1", game))
```

@@

```{r}
simple_baselines = baseline_data %>% 
  filter(policy == "optimal") %>%
  group_by(game_type) %>%
  summarize(expected_reward = mean(expected_reward)) %>%
  ungroup()

summary_plot(reward_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

    pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
      geom_point() +
      geom_text(aes(label=task)) +
      guides(color=F)
    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)
